### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:18	20:59:26	(Tue18.Mar)

\ans{The reviewer is absolutely right. The copy will be serialized due to divergent branching. It is unfortunate that to the best of our knowledge no Cholesky based batch linear equation solver exist, which would have eliminated the need for the lower triangular... The paragraph has been edited to explain this better.}

@@

\ai{We indeed presteer all the elements. To make this clearer we have now stated it again after equation (2), and explained that a generalization is straight forward by substituting $\1$ with a steering vector.}

>>>>

\ans{The reviewer is absolutely right. The copy will be serialized due to divergent branching. It is unfortunate that to the best of our knowledge no Cholesky based batch linear equation solver exist, which would have eliminated the need for the lower triangular. The paragraph has been edited to explain this better.}

@@

\ai{We indeed presteer all the elements to deal with with our wideband signal. To make this clearer we have now stated it again after equation (2), and explained that in a narrowband case a generalization is straight forward by substituting $\1$ with a steering vector.}
